Covariate analysis of MSBB microarray data

### 2015-12-31 code/Rmd/MSSM_Array.Rmd
Minor fix

  return(list(EXPR = expr,
              COVAR = covar,
              FIT = fit, 
              RESIDUAL = residualFit, 
              DESIGN = DESIGN, 
              ANNOTATIONS = ANNOTATIONS))
}
```
### Middle Temporal Analysis
```{r middle.temporal, cache=TRUE, fig.height=10, fig.width=15}
# SynIDs of expression and covariates matrix
EXP_ID <- c('Middle Temporal' = 'syn3191101',
            'Superior Temporal' = 'syn3191103',
            'Inferior Temporal' = 'syn3191099',
            'Superior Parietal Lobule' = 'syn3191119',
            'Caudal Anterior Cingulate' = 'syn3191107',
            'Parahippocampal Gyrus' = 'syn3191109',
            'Frontal Pole' = 'syn3191107')
COV_ID <- 'syn3205399'

>>>>

  return(list(EXPR = expr,
              COVAR = covar,
              FIT = fit, 
              RESIDUAL = residualFit, 
              DESIGN = DESIGN, 
              ANNOTATIONS = ANNOTATIONS))
}
```
### Extract adjust covariates
```{r middle.temporal, cache=TRUE, fig.height=10, fig.width=15}
# SynIDs of expression and covariates matrix
EXP_ID <- c('Middle Temporal' = 'syn3191101',
            'Superior Temporal' = 'syn3191103',
            'Inferior Temporal' = 'syn3191099',
            'Superior Parietal Lobule' = 'syn3191119',
            'Caudal Anterior Cingulate' = 'syn3191107',
            'Parahippocampal Gyrus' = 'syn3191109',
            'Frontal Pole' = 'syn3191107')
COV_ID <- 'syn3205399'
